### 2019-04-08 4_implementation.tex
Trimming some text to make things fit again.

In the DTD model, tasks are enumerated in program order (by
executing the program), and dependencies between tasks are
identified automatically based on the input and output data of tasks. 
A task depends on another task if it reads data written by the other task,
and the data is copied automatically if the two tasks are executed on
different nodes. To
improve horizontal scalability, the program is executed in
SPMD fashion on all nodes, and the user is responsible for eliding
tasks that are not directly connected to those that are to be executed
on the current node.

@@

Regent~\cite{Regent15} is an implicitly-parallel task-based language
which implements the Legion programming model~\cite{Legion12}. We use
Regent rather than Legion directly because the Regent compiler
provides a critical optimization, \emph{control replication}, that
enables superior horizontal scalability~\cite{ControlReplication17}.

@@

Spark~\cite{Spark10} is an implicitly-parallel programming model for
data analytics, widely used in industrial data center applications. As
one of the programming models in this study not originally intended
for scientific computing, Spark makes very different tradeoffs from
other systems under consideration, and therefore makes an interesting
point of comparison.

@@

StarPU~\cite{StarPU11} is a task-based system that supports a \emph{sequential task flow} (STF)
programming model similar to PaRSEC's DTD. Our Task Bench implementation in
StarPU is very similar to PaRSEC, including the use of a switch
statement to handle dynamic numbers of task dependencies and manual
elision of tasks on unrelated nodes to provide horizontal scalability.
We use a simplified version of the 2D block cyclic data distribution from the Chameleon 
project~\cite{Chameleon}.

>>>>

In the DTD model, tasks are enumerated in program order (by
executing the program), and dependencies between tasks are
identified automatically based on the input and output data of tasks. 
A task depends on another task if it reads data written by the other task,
and the data is copied automatically if the two tasks are executed on
different nodes. To
improve scalability, the program is executed in
SPMD fashion on all nodes, and the user is responsible for eliding
tasks that are not directly connected to those that are to be executed
on the current node.

@@

Regent~\cite{Regent15} is an implicitly-parallel task-based language
which implements the Legion programming model~\cite{Legion12}. We use
Regent rather than Legion directly because the Regent compiler
provides a critical optimization, \emph{control replication}, that
enables superior scalability~\cite{ControlReplication17}.

@@

Spark~\cite{Spark10} is an implicitly-parallel programming model for
large scale data analytics. As
one of the programming models in this study not originally intended
for scientific computing, Spark makes very different tradeoffs from
other systems under consideration, and therefore makes an interesting
point of comparison.

@@

StarPU~\cite{StarPU11} is a task-based system that supports a \emph{sequential task flow} (STF)
programming model similar to PaRSEC's DTD. Our Task Bench implementation in
StarPU is very similar to PaRSEC, including the use of a switch
statement to handle dynamic numbers of task dependencies and manual
elision of tasks on unrelated nodes to improve scalability.
We use a simplified version of the 2D block cyclic data distribution from the Chameleon 
project~\cite{Chameleon}.
